### 2018-10-11 doc/paper.tex
Minor updates.

When pointwise interpolation is used to transfer a solution, quantities with
physical meaning (e.g. mass, concentration, energy) may not be conserved.
To address this, there have been many explorations of
\emph{conservative interpolation}. Since solution transfer is so commonly
needed in physical applications, this problem of conservative interpolation
has been considered already for straight sided meshes.
However, both to allow for greater
geometric flexibility and for high order of convergence, this paper will
consider the case of curved isoparametric\footnote{I.e. the degree of the
discrete field on the mesh is same as the degree of the shape functions that
determine the mesh.} meshes. Allowing curved geometries is useful since
many practical
problems involve geometries that change over time, such as flapping flight
or fluid-structure interactions. In addition, high-order CFD methods
have the ability to produce highly accurate solutions
with low dissipation and low dispersion error.

@@

Lagrangian methods treat each point in the
physical domain as a ``particle'' which moves along a characteristic curve
over time and then monitor values associated with the particle (heat / energy,
velocity, pressure, density, concentration, etc.). They are an effective way
to solve PDEs, even with higher order or non-linear terms.

This approach transforms the numerical solution of PDEs into a family of
numerical solutions to many independent ODEs. It allows the use of familiar
and well understood ODE solvers. In addition, Lagrangian methods often
have less restrictive conditions on time steps than Eulerian
methods\footnote{In Eulerian methods, the mesh is fixed.}.
When solving PDEs on unstructured meshes
with Lagrangian methods, the nodes move (since they
are treated like particles) and the mesh ``travels''.

A flow-based change to a mesh can cause problems if it causes the mesh to
leave the domain being analyzed or if it distorts the mesh until the element
quality is too low in some mesh elements. Over enough time, the mesh can
even tangle (i.e. elements begin to overlap).

>>>>

When pointwise interpolation is used to transfer a solution, quantities with
physical meaning (e.g. mass, concentration, energy) may not be conserved.
To address this, there have been many explorations of
\emph{conservative interpolation}. Since solution transfer is so commonly
needed in physical applications, this problem of conservative interpolation
has been considered already for straight sided meshes.
However, both to allow for greater
geometric flexibility and for high order of convergence, this paper will
consider the case of curved isoparametric\footnote{I.e. the degree of the
discrete field on the mesh is same as the degree of the shape functions that
determine the mesh.} meshes. High-order methods
have the ability to produce highly accurate solutions
with low dissipation and low dispersion error, however, they typically
require curved meshes. In addition, curved elements have
advantages in problems that involve geometries that change over time,
such as flapping flight or fluid-structure interactions.

@@

Lagrangian methods treat each point in the
physical domain as a ``particle'' which moves along a characteristic curve
over time and then monitor values associated with the particle (heat / energy,
velocity, pressure, density, concentration, etc.). They are an effective way
to solve PDEs, even with higher order or non-linear terms \cite{MR3023731}.
This approach transforms the numerical solution of PDEs into a family of
numerical solutions to many independent ODEs. It allows the use of familiar
and well understood ODE solvers. In addition, Lagrangian methods often
have less restrictive conditions on time steps than Eulerian
methods\footnote{In Eulerian methods, the mesh is fixed.}.
When solving PDEs on unstructured meshes
with Lagrangian methods, the nodes move (since they
are treated like particles) and the mesh ``travels''.
A flow-based change to a mesh can cause problems if it causes the mesh to
leave the domain being analyzed or if it distorts the mesh until the element
quality is too low in some mesh elements. Over enough time, the mesh can
even tangle (i.e. elements begin to overlap).
